---
title: "SMSCG Comparision"
author: "Michelle Nelson"
date: "2024-01-25"
output: html_document
---

# Overview
The goal of this comparison is to compare the two sets of sites that SMSCG uses to monitor the action plan. 
The comparison will be between: Hunter Cut (HUN)vs Montezuma Buoy (GZM) and Grizzly Bay Buoy (GZB)vs Grizzly Bay Pile (GZL)


```{r}
### make sure you have the right libraries installed: tidyverse, etc
```
1. libraries 
```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.show = "hide")


library(tidyverse)
library("ggpubr")
library(lubridate)
library(wql)
library(RColorBrewer)
library(cder)
library(dplyr)
library(readr)
library(here)
source(here("helpful_functions.R"))
```

#2 Load in data. Now I have 6 different data frames for all the data needed(4 years of comparisions with 2018 being on one 2 site comparision)
```{r}
### Load in the data running these functions #make sure to run Helpful r functions 1st!

dfGZLediALL <- get_edi_file(1177, "GZL")[[1]]

dfGZLediALL <- dfGZLediALL %>% filter(year(date)>=2018)

dfGZBfinal <- abs_path_emp("Water Quality/SMSCG/GZB_final.csv")%>% read.csv(.)

dfHUNALL <- abs_path_emp("Water Quality/SMSCG/HUN_All.csv")%>% read.csv(.)

dfGZMALL <- abs_path_emp("Water Quality/SMSCG/GZM_All.csv")%>% read.csv(.)

df_GZL2023 <- abs_path_emp("Water Quality/SMSCG/GZL_2023_data.csv")%>% read.csv(.)

dfGZB <- abs_path_emp("Water Quality/SMSCG/GZB_data.csv")%>% read.csv(.)


### tried this code got an error: GZB_2024 <- abs_path_emp("Water Quality/SMSCG/GZB_2024.csv")%>% read.csv(.)

#got from chat gpt didnt work #GZB_2024 <- abs_path_emp("Water Quality/SMSCG/GZB_2024.csv") %>% 
#  read.csv(., fileEncoding = "UTF-8")
###GZB_2024 <- abs_path_emp("Water Quality/SMSCG/GZB_2024.csv") %>% 
  ##read.csv(., fileEncoding = "latin1")

## read in but long view not wide view vivian will work on separately and then we will read the file back in later. 


## below is the old way that I pulled in the data
#GZB
#dfGZB <- read.csv("C:/Users/nelsonm/OneDrive - California Department of Water Resources/R/SMSCG Comparision/GZB_data.csv")
#view(dfGZB)
## the above 2 have no QC flags all good data
######2021
# GZB
#dfGZBfinal <- read.csv("C:/Users/nelsonm/OneDrive - California Department of Water Resources/R/SMSCG Comparision/GZB_final.csv")
#view(dfGZBfinal) ## does have QC flags need to filter for good data
#GZL
#df_GZLediALL
#HUN
#dfHUNALL <- read.csv("C:/Users/nelsonm/OneDrive - California Department of Water Resources/R/SMSCG Comparision/HUN_All.csv") 
#view(dfHUNALL) ## does have QC flags need to filter for good data
# GZM
#DFGZMALL <- read.csv("C:/Users/nelsonm/OneDrive - California Department of Water Resources/R/SMSCG Comparision/GZM_All.csv")
#view (DFGZMALL)

##### 2022
#GZB 
#dfGZBfinal
#GZL
#df_GZLediALL
#HUN
#dfHUNALL
#GZM
#DFGZMALL

##### 2023
#GZB
#dfGZBfinal
#GZL
#df_GZL2023 <- read.csv("C:/Users/nelsonm/OneDrive - California Department of Water Resources/R/SMSCG Comparision/GZL_2023_data.csv")
#view(df_GZL2023) ### no flagged data all good
#HUN
#dfHUNALL
#GZM
#DFGZMALL



```

#3 reformat dates
```{r}
###GZL2018

dfGZLediALL <- dfGZLediALL %>% mutate(date_time = paste(date, time)) %>% #combine the date and time columns
  mutate(year = year(date_time)) #add a year column

view(dfGZLediALL)## all good need to model all other dataframes like this one (column order, names, remove bad qcd data etc)


###GZB2018 is dfGZB

### 2021 all 4 stations
#dfGZBfinal <- dfGZBfinal %>%
 # mutate(year = year(date_time)) ## this didnt work this is what cGPT said :I apologize for the confusion. If your date_time column is in a format that R recognizes, you should not use as.POSIXct with paste to convert it. It seems there might be an issue with how the date and time are represented in your original data.If your date_time column is in a character format and you need to parse it into a datetime object, you can use ymd_hms from the lubridate package, which handles parsing date-time strings in various formats.
#dfGZBfinal <- dfGZBfinal %>%
 # mutate(date_time = ymd_hms(date_time),
  #       year = year(date_time)) ## more problems cGPT said to manually specify format

#dfGZBfinal3yrs <- dfGZBfinal %>%
 # mutate(date_time = as.POSIXct(date_time, format = '%m/%d/%Y %H:%M', tz = 'UTC'),
  #       year = year(date_time)) ## didnt work checking colnames
#colnames(dfGZBfinal)

## trying this code to match column name
dfGZBfinal3yrs <- dfGZBfinal %>% 
  mutate(DATETIME = as.POSIXct(DATETIME, format = '%m/%d/%Y %H:%M', tz = 'UTC'),
         year = year(DATETIME))
view(dfGZBfinal3yrs)


## GZL already done for 2018, 2021, 2022 will need 2023 below

##HUN
dfHUNALL3 <- dfHUNALL %>%
  mutate(DATETIME = as.POSIXct(DATETIME, format = '%m/%d/%Y %H:%M', tz = 'UTC'),
         year = year(DATETIME)) ### this worked! just needed to see that the original datetime didnt have seconds and same column name
View(dfHUNALL3)

### GZM all years 21-23

dfGZMALL3 <- dfGZMALL %>%
  mutate(DATETIME = as.POSIXct(DATETIME, format = '%m/%d/%Y %H:%M', tz = 'UTC'),
         year = year(DATETIME))
view(dfGZMALL)

## last one needed dates cleaned GZL 2023, this one does have the seconds in the original datetime
 
 df_GZL2023<- df_GZL2023 %>%
 mutate(date_time = as.POSIXct(paste(date, time), format = '%m/%d/%Y %H:%M:%S')) %>%
  mutate(year = year(date_time)) 
 view(df_GZL2023)
 ## now all dates should be the same so I can combine the full dataset later
 dfGZBfinal <- dfGZBfinal %>% mutate(DATE.TIME = as.POSIXct(DATETIME, format = "%Y-%m-%d %H:%M:%S"))
dfGZLediALL <-dfGZLediALL %>% mutate(date_time = as.POSIXct(date_time, format = "%Y-%m-%d %H:%M:%S"))
df_GZL2023 <- df_GZL2023 %>% mutate(date_time = as.POSIXct(date_time, format = "%Y-%m-%d %H:%M:%S"))
dfGZBfinal3yrs <- dfGZBfinal3yrs %>% mutate(DATETIME = as.POSIXct(DATETIME, format = "%Y-%m-%d %H:%M:%S"))
dfGZMALL3 <- dfGZMALL3 %>% mutate(DATETIME = as.POSIXct(DATETIME, format = "%Y-%m-%d %H:%M:%S"))
dfHUNALL3 <- dfHUNALL3 %>% mutate(DATETIME = as.POSIXct(DATETIME, format = "%Y-%m-%d %H:%M:%S"))

view(df_GZBFINAL)
## will need to rename datetime in last 3 to the same as first three above can do when cleaning data and ordering column names
## not sure if this was done later or not...

```
#4 clean out bad data from WQA datasets
-Replace all values that have Bad ("B" and "X") codes with NAs

```{r}

## from looking at the file it looks like all X code has NAs, should double check though somehow
# three WQA datasets: 

# dfGZBfinal3yrs
colnames(dfGZBfinal3yrs)


#check fluor first
unique(dfGZBfinal3yrs$Chl...QAQC.Flag) ## has all 4 codes want to make sure first that there isnt a lot of unchecked data.
## just showed me the flag types
#Chl_a_ug_L_counts <- dfGZBfinal3yrs %>%
 # group_by(Chl...QAQC.Flag) %>%
  #summarise(NumDistinctFlags = n_distinct(Chl...QAQC.Flag))
#View(Chl_a_ug_L_counts)

##Chl_a_ug_L_counts <- dfGZBfinal3yrs %>%
#  group_by(Chl...QAQC.Flag) %>%
 # summarise(NumOccurrences = n())
#view(Chl_a_ug_L_counts)

#flourescence changing all B,X and U flags to NAs ####THIS WORKED REPLACING VALUES WITH NA

dfGZBfinal3yrs <- dfGZBfinal3yrs %>%
  mutate(across(everything(), ~ifelse(Chl.SOP.Process.QC.Flag %in% c('U', 'X', 'M', 'B'), NA, .)))


summary(dfGZBfinal3yrs)



dfGZBfinal3yrs$Chl.a..µg.L. <- replace(dfGZBfinal3yrs$Chl.a..µg.L., dfGZBfinal3yrs$Chl...QAQC.Flag=="B", NA)
dfGZBfinal3yrs$Chl.a..µg.L. <- replace(dfGZBfinal3yrs$Chl.a..µg.L., dfGZBfinal3yrs$Chl...QAQC.Flag=="X", NA)
dfGZBfinal3yrs$Chl.a..µg.L. <- replace(dfGZBfinal3yrs$Chl.a..µg.L., dfGZBfinal3yrs$Chl...QAQC.Flag=="U", NA)

#turbidity # the colnames are ridiculous should replace now but didnt
dfGZBfinal3yrs$Turbidity..NTU. <- replace(dfGZBfinal3yrs$Turbidity..NTU., dfGZBfinal3yrs$Turbidity...QAQC.Flag=="B", NA)
dfGZBfinal3yrs$Turbidity..NTU. <- replace(dfGZBfinal3yrs$Turbidity..NTU., dfGZBfinal3yrs$Turbidity...QAQC.Flag=="X", NA)
dfGZBfinal3yrs$Turbidity..NTU. <- replace(dfGZBfinal3yrs$Turbidity..NTU., dfGZBfinal3yrs$Turbidity...QAQC.Flag=="U", NA)

###Spc
dfGZBfinal3yrs$SpCond..µS.cm. <- replace(dfGZBfinal3yrs$SpCond..µS.cm.,dfGZBfinal3yrs$SpCond...QAQC.Flag                                           =="B", NA)
dfGZBfinal3yrs$SpCond..µS.cm. <- replace(dfGZBfinal3yrs$SpCond..µS.cm.,dfGZBfinal3yrs$SpCond...QAQC.Flag                                           =="X", NA)
dfGZBfinal3yrs$SpCond..µS.cm. <- replace(dfGZBfinal3yrs$SpCond..µS.cm.,dfGZBfinal3yrs$SpCond...QAQC.Flag                                           =="U", NA)

#### temp
dfGZBfinal3yrs$Temp...C. <- replace(dfGZBfinal3yrs$Temp...C., dfGZBfinal3yrs$Temp...QAQC.Flag=="B", NA)
dfGZBfinal3yrs$Temp...C. <- replace(dfGZBfinal3yrs$Temp...C., dfGZBfinal3yrs$Temp...QAQC.Flag=="X", NA)
dfGZBfinal3yrs$Temp...C. <- replace(dfGZBfinal3yrs$Temp...C., dfGZBfinal3yrs$Temp...QAQC.Flag=="U", NA)


### pH
dfGZBfinal3yrs$pH <- replace(dfGZBfinal3yrs$pH, dfGZBfinal3yrs$pH...QAQC.Flag=="B", NA)
dfGZBfinal3yrs$pH <- replace(dfGZBfinal3yrs$pH, dfGZBfinal3yrs$pH...QAQC.Flag=="X", NA)
dfGZBfinal3yrs$pH <- replace(dfGZBfinal3yrs$pH, dfGZBfinal3yrs$pH...QAQC.Flag=="U", NA)
### DO
dfGZBfinal3yrs$DO..mg.L. <- replace(dfGZBfinal3yrs$DO..mg.L.,dfGZBfinal3yrs$DO...QAQC.Flag=="B", NA)
dfGZBfinal3yrs$DO..mg.L. <- replace(dfGZBfinal3yrs$DO..mg.L.,dfGZBfinal3yrs$DO...QAQC.Flag=="X", NA)
dfGZBfinal3yrs$DO..mg.L. <- replace(dfGZBfinal3yrs$DO..mg.L.,dfGZBfinal3yrs$DO...QAQC.Flag=="U", NA)

#### DFGZMALL
#temp
dfGZMALL3$Temp...C. <- replace(dfGZMALL3$Temp...C., dfGZMALL3$Temp...QAQC.Flag=="B", NA)
dfGZMALL3$Temp...C. <- replace(dfGZMALL3$Temp...C., dfGZMALL3$Temp...QAQC.Flag=="X", NA)
dfGZMALL3$Temp...C. <- replace(dfGZMALL3$Temp...C., dfGZMALL3$Temp...QAQC.Flag=="U", NA)
#spc
dfGZMALL3$SpCond..µS.cm. <- replace(dfGZMALL3$SpCond..µS.cm., dfGZMALL3$SpCond...QAQC.Flag=="B", NA)
dfGZMALL3$SpCond..µS.cm. <- replace(dfGZMALL3$SpCond..µS.cm., dfGZMALL3$SpCond...QAQC.Flag=="X", NA)
dfGZMALL3$SpCond..µS.cm. <- replace(dfGZMALL3$SpCond..µS.cm., dfGZMALL3$SpCond...QAQC.Flag=="U", NA)
#DO
dfGZMALL3$DO..mg.L. <- replace(dfGZMALL3$DO..mg.L.,dfGZMALL3$DO...QAQC.Flag=="B", NA)
dfGZMALL3$DO..mg.L. <- replace(dfGZMALL3$DO..mg.L.,dfGZMALL3$DO...QAQC.Flag=="X", NA)
dfGZMALL3$DO..mg.L. <- replace(dfGZMALL3$DO..mg.L.,dfGZMALL3$DO...QAQC.Flag=="U", NA)
#ph
dfGZMALL3$pH <- replace(dfGZMALL3$pH, dfGZMALL3$pH...QAQC.Flag=="B", NA)
dfGZMALL3$pH <- replace(dfGZMALL3$pH, dfGZMALL3$pH...QAQC.Flag=="X", NA)
dfGZMALL3$pH <- replace(dfGZMALL3$pH, dfGZMALL3$pH...QAQC.Flag=="U", NA)
#turb
dfGZMALL3$Turbidity..NTU. <- replace(dfGZMALL3$Turbidity..NTU., dfGZMALL3$Turbidity...QAQC.Flag=="B", NA)
dfGZMALL3$Turbidity..NTU. <- replace(dfGZMALL3$Turbidity..NTU., dfGZMALL3$Turbidity...QAQC.Flag=="X", NA)
dfGZMALL3$Turbidity..NTU. <- replace(dfGZMALL3$Turbidity..NTU., dfGZMALL3$Turbidity...QAQC.Flag=="U", NA)
#fluor
dfGZMALL3$Chl.a..µg.L. <- replace(dfGZMALL3$Chl.a..µg.L., dfGZMALL3$Chl...QAQC.Flag=="B", NA)
dfGZMALL3$Chl.a..µg.L. <- replace(dfGZMALL3$Chl.a..µg.L., dfGZMALL3$Chl...QAQC.Flag=="X", NA)
dfGZMALL3$Chl.a..µg.L. <- replace(dfGZMALL3$Chl.a..µg.L., dfGZMALL3$Chl...QAQC.Flag=="U", NA)

view(dfGZMALL3)

selected_column <- 'Chl...QAQC.Flag'

cat("Summary for", selected_column, ":\n")
print(table(dfGZMALL3[[selected_column]]))
#### just realized there is no B code for WQA annoying
##HUNALL3
#temp
dfHUNALL3$Temp...C. <- replace(dfHUNALL3$Temp...C., dfHUNALL3$Temp...QAQC.Flag=="X", NA)
dfHUNALL3$Temp...C. <- replace(dfHUNALL3$Temp...C., dfHUNALL3$Temp...QAQC.Flag=="U", NA)
#spc
dfHUNALL3$SpCond..µS.cm. <- replace(dfHUNALL3$SpCond..µS.cm., dfHUNALL3$SpCond...QAQC.Flag=="X", NA)
dfHUNALL3$SpCond..µS.cm. <- replace(dfHUNALL3$SpCond..µS.cm., dfHUNALL3$SpCond...QAQC.Flag=="U", NA)
##DO
dfHUNALL3$DO..mg.L. <- replace(dfHUNALL3$DO..mg.L., dfHUNALL3$DO...QAQC.Flag=="X", NA)
dfHUNALL3$DO..mg.L. <- replace(dfHUNALL3$DO..mg.L., dfHUNALL3$DO...QAQC.Flag=="U", NA)
##ph
dfHUNALL3$pH <- replace(dfHUNALL3$pH, dfHUNALL3$pH...QAQC.Flag=="X", NA)
dfHUNALL3$pH <- replace(dfHUNALL3$pH, dfHUNALL3$pH...QAQC.Flag=="U", NA)
##turb
dfHUNALL3$Turbidity..NTU. <- replace(dfHUNALL3$Turbidity..NTU., dfHUNALL3$Turbidity...QAQC.Flag=="X", NA)
dfHUNALL3$Turbidity..NTU. <- replace(dfHUNALL3$Turbidity..NTU., dfHUNALL3$Turbidity...QAQC.Flag=="U", NA)
##fluor
dfHUNALL3$Chl.a..µg.L. <- replace(dfHUNALL3$Chl.a..µg.L., dfHUNALL3$Chl...QAQC.Flag=="X", NA)
dfHUNALL3$Chl.a..µg.L. <- replace(dfHUNALL3$Chl.a..µg.L., dfHUNALL3$Chl...QAQC.Flag=="U", NA)

selected_column <- 'Chl...QAQC.Flag'

cat("Summary for", selected_column, ":\n")
print(table(dfHUNALL3[[selected_column]]))

view(dfHUNALL3)
```
#5 should arrange colnames and take out slopes and QC flag columns

```{r}
### remove unwanted columns in WQA and rename to CEMP file column names
colnames(dfHUNALL3)
# Assuming 'dfHUNALL3', 'dfGZMALL3', and 'dfGZBfinal3years' are your DataFrames
# Replace these with your actual DataFrames or load them from files

# List of columns to be kept
columns_to_keep <- c("STATION.NAME", "DATETIME", "DO..mg.L.", "SpCond..µS.cm.", "pH", "Temp...C.", "Turbidity..NTU.", "Chl.a..µg.L.")

# Load the dplyr package if not already loaded
# install.packages("dplyr")
library(dplyr)

# Function to keep specified columns in a dataframe and rename it
keep_columns_and_rename <- function(df, columns, new_name_suffix) {
  new_name <- paste0(deparse(substitute(df)), new_name_suffix)
  return(assign(new_name, df %>% select(all_of(columns)), envir = .GlobalEnv))
}

# Keep specified columns in each dataframe and rename them
dfHUNALL3F <- keep_columns_and_rename(dfHUNALL3, columns_to_keep, "F")
dfGZMALL3F <- keep_columns_and_rename(dfGZMALL3, columns_to_keep, "F")
dfGZBfinal3yrsF <- keep_columns_and_rename(dfGZBfinal3yrs, columns_to_keep, "F")


```
#6 rename colnames in WQA to match CEMP add date time year col

```{r}
# wanted column names
colnames(df_GZL2023)
# New column names
new_column_names <- c("station", "date_time", "dissolvedoxygen", "spc", "ph", "watertemperature", "turbidity", "fluorescence")

# Function to rename columns in a dataframe
rename_columns <- function(df, new_names) {
  colnames(df) <- new_names
  return(df)
}

# Rename columns in each dataframe

dfHUNALL3F <- rename_columns(dfHUNALL3F, new_column_names)
dfGZMALL3F <- rename_columns(dfGZMALL3F, new_column_names)
dfGZBfinal3yrsF <- rename_columns(dfGZBfinal3yrsF, new_column_names)

## add date, time, year col to match CEMP

library(dplyr)

# Function to add new date, time, and year columns based on the DateTime column
add_datetime_columns <- function(df) {
  df <- df %>%
    mutate(date = as.Date(date_time),
           time = format(date_time, "%H:%M:%S"),
           year = lubridate::year(date_time))
  return(df)
}

# Add new date, time, and year columns to each dataframe
dfHUNALL3F <- add_datetime_columns(dfHUNALL3F)
dfGZMALL3F <- add_datetime_columns(dfGZMALL3F)
dfGZBfinal3yrsF <- add_datetime_columns(dfGZBfinal3yrsF)


```

#7 make sure columns in same order
```{r}


# Reference order of columns
reference_order <- c("date_time", "date", "time", "year", "station", "dissolvedoxygen", "spc", "ph", "watertemperature", "turbidity", "fluorescence")

# Load the dplyr package if not already loaded
# install.packages("dplyr")
library(dplyr)

# Function to rearrange columns in a dataframe based on reference order
rearrange_columns <- function(df, reference_order) {
  df <- select(df, all_of(reference_order))
  return(df)
}

# Rearrange columns in each dataframe
dfHUNALL3F <- rearrange_columns(dfHUNALL3F, reference_order)
dfGZMALL3F <- rearrange_columns(dfGZMALL3F, reference_order)
dfGZBfinal3yrsF <- rearrange_columns(dfGZBfinal3yrsF, reference_order)
dfGZBFINAL <- rearrange_columns(dfGZB, reference_order)
dfGZLediALL <- rearrange_columns(dfGZLediALL, reference_order)
df_GZL2023 <- rearrange_columns(df_GZL2023, reference_order)


### need to change WQA station names to acronyms
## never did this
## cant get this to work without adding a column dfHUNALL3F <- dfHUNALL3F %>%
 ## mutate(station = if_else(station == "Hunter Cut", "HUN", station))


```


#8 need to add new data from 2024 GZM, HUN, GZL, GZB- repeat steps from #2
```{r}
GZM24 <- abs_path_emp("Water Quality/SMSCG/GZM_2024_CLEANEDDATA.csv")%>% read.csv(.)
GZB24 <- abs_path_emp("Water Quality/SMSCG/GZB_2024_CLEANED DATA.csv")%>% read.csv(.)
HUN24 <- abs_path_emp("Water Quality/SMSCG/HUN_2024_CLEANED DATA.csv")%>% read.csv(.)


```



#9 combine all dataframes
```{r}
## make sure dates are all the same character type


library(dplyr)


library(lubridate)

# Convert date_time columns to POSIXct type with consistent format and remove unwanted columns/ reorder the rest right after:

dfGZBFINAL <- dfGZBFINAL %>% mutate(date_time = as.POSIXct(paste(date_time, "00:00:00"), format = "%Y-%m-%d %H:%M:%S")) #date
dfGZBFINAL2 <- dfGZBFINAL %>%  select(-date, -time, -year) #removing columns
str(dfGZBFINAL2)

dfGZLediALL <- dfGZLediALL %>% mutate(date_time = as.POSIXct(date_time, format = "%Y-%m-%d %H:%M:%S"))
dfGZLediALL2 <- dfGZLediALL %>%  select(-date, -time, -year) #removing columns



df_GZL2023 <- df_GZL2023 %>% mutate(date_time = as.POSIXct(date_time, format = "%Y-%m-%d %H:%M:%S"))
df_GZL20232 <- df_GZL2023 %>%  select(-date, -time, -year) #removing columns
str(df_GZL20232)


str(dfGZBfinal3yrsF)
head(dfGZBfinal3yrsF)
dfGZBfinal3yrs2 <- dfGZBfinal3yrsF %>% select(-date, -time, -year) ## wont run keeps making the new DF have no data
## trying to kepp the columns I want. 
dfGZBfinal3yrs2 <- dfGZBfinal3yrsF %>% select(date_time, station, dissolvedoxygen, spc, ph, turbidity, fluorescence)
dfGZBfinal3yrs2<- dfGZBfinal3yrs2 %>% mutate(date_time = as.POSIXct(date_time, format = "%Y-%m-%d %H:%M:%S"))


###
dfGZMALL3F <- dfGZMALL3F %>% select(-date, -time, -year)
dfGZMALL3F <- dfGZMALL3F %>% select(date_time, station, dissolvedoxygen, spc, ph, turbidity, fluorescence)
dfGZMALL3F <- dfGZMALL3F %>% mutate(date_time = as.POSIXct(date_time, format = "%Y-%m-%d %H:%M:%S"))

####

dfHUNALL3F <- dfHUNALL3F %>% select(-date, -time, -year)
dfHUNALL3F <- dfHUNALL3F %>% select(date_time, station, dissolvedoxygen, spc, ph, turbidity, fluorescence)
dfHUNALL3F <- dfHUNALL3F %>% mutate(date_time = as.POSIXct(date_time, format = "%Y-%m-%d %H:%M:%S"))




##dfGZMALL3F <- dfGZMALL3F %>% mutate(date_time = as.POSIXct(date_time, format = "%Y-%m-%d %H:%M:%S"))

##dfHUNALL3F <- dfHUNALL3F %>% mutate(date_time = as.POSIXct(date_time, format = "%Y-%m-%d %H:%M:%S"))

# Ensure consistent time format
#df_GZBFINAL <- df_GZBFINAL %>% mutate(time = format(date_time, format = "%H:%M:%S"))
#str(df_GZBFINAL)
#df_GZLediALL <- df_GZLediALL %>% mutate(time = format(date_time, format = "%H:%M:%S"))
#df_GZL2023 <- df_GZL2023 %>% mutate(time = format(date_time, format = "%H:%M:%S"))
#dfGZBfinal3yrsF <- dfGZBfinal3yrsF %>% mutate(date_time = format(date_time, format = "%H:%M:%S"))
#dfGZMALL3F <- dfGZMALL3F %>% mutate(time = format(date_time, format = "%H:%M:%S"))
#dfHUNALL3F <- dfHUNALL3F %>% mutate(time = format(date_time, format = "%H:%M:%S"))





# Combine the dataframes using bind_rows
combined_df <- bind_rows(dfGZBFINAL2, dfGZLediALL2, df_GZL20232, dfGZBfinal3yrs2, dfGZMALL3F, dfHUNALL3F)

###### YAY IT WORKED

###Now I want to rename the station

unique(combined_df$station)

# Rename specific stations
combined_df <- combined_df %>%
  mutate(station = case_when(
    station == "Grizzly Bay East" ~ "GZB",
    station == "Montezuma Slough Mouth" ~ "GZM",
    station == "Hunter Cut" ~ "HUN",
    TRUE ~ station  # Keep other stations unchanged
  ))

unique(combined_df$station)

#### write csv of combined_df for saving?
###write.csv(combined_df, file = "C:/Users/nelsonm/OneDrive - California Department of Water Resources/R/SMSCG Comparision/combined_data.csv", row.names = FALSE)
```
 #10 comparision 2018 GZL and GZB 
 
```{r}
library(dplyr)
library(lubridate)
library(ggplot2)

str(combined_df)

filtered_dataGZL <- combined_df %>% 
  filter(station == "GZL",
         date_time >=as.Date("2018-07-01"),
         date_time<=as.Date("2018-10-06"))


  
GZL2018<-ggplot(data = filtered_dataGZL, aes(x = date_time, y = spc )) + geom_line(color = "red") + labs(title = "GZL Specific conductivity gate action 2018", 
                                 x = "Date", y = "Specific Conductivity") + theme_minimal()

print(GZL2018)


ggplot(data = filtered_dataGZL, aes(x = date_time, y = watertemperature )) + geom_line(color = "blue") + labs(title = "GZL Water Temperature gate action 2018", 
                                 x = "Date", y = "Water Temperature") + theme_minimal()

```
```{r}
### lets see what the two sites look like plotted together

filtered_dataGZLGZB <- combined_df %>% 
  filter(station == c("GZL", "GZB"),
         date_time >=as.Date("2018-07-01"),
         date_time <=as.Date("2018-10-06"))


  
ggplot(data = filtered_dataGZLGZB, aes(x = date_time, y = spc, color = station )) + geom_line() +geom_point() + labs(title = "GZL and GZB Specific conductivity gate action 2018", x = "Date", y = "Specific Conductivity", color = "Station") + theme_minimal()


ggplot(data = filtered_dataGZLGZB, aes(x = date_time, y = spc, color = station )) + geom_line() + labs(title = "GZL and GZB Specific conductivity gate action 2018", x = "Date", y = "Specific Conductivity", color = "Station") + theme_minimal()

###decided to put all comparision sites together on plots per parameter below is working code, may want to just smooth out the line and tweak the way the plots look but continue to

###ENDED HERE didnt look at any code past this
```


#11 QQPLOTS per parameter for each station

```{r}
# Load ggplot2 library
library(ggplot2)
### in order to do QQplots/facet_grid I need to reshape the data into long format
library(tidyr)

# Reshaping data to long format
combined_df_long <- combined_df %>%
  pivot_longer(
    cols = c(dissolvedoxygen, spc, ph, watertemperature, turbidity, fluorescence),
    names_to = "Parameter",
    values_to = "Value"
  )

###missing or NA values
combined_df_long <- na.omit(combined_df_long)



# Generate QQ Plots

## overall ggplot(combined_df_long, aes(sample = Value)) + 
##  stat_qq() +
  ##stat_qq_line(color = "red") +
  ##facet_grid(Parameter ~ station) +  # Rows: Parameters, Columns: Stations
  ##labs(
    ##title = "QQ Plots for Water Quality Data",
  #  x = "Theoretical Quantiles",
   # y = "Sample Quantiles"
  #) +
  #theme_minimal()

##above was comparing to all parameters to all parameters need to do individual parameters
## at all stations



#DO
# Assuming 'combined_df_long' is your long-format dataframe
parameter_to_plot <- "dissolvedoxygen"  # Replace with your desired parameter

# Subset the data for the chosen parameter
subset_dfDO <- combined_df_long[combined_df_long$Parameter == parameter_to_plot, ]

# Generate QQ plots for the chosen parameter across all stations
(ggplot(subset_dfDO, aes(sample = Value)) +
  stat_qq() +
  stat_qq_line(color = "red") +
  facet_wrap(~station, scales = "free") +  # One plot per station
  labs(
    title = paste("QQ Plots for", parameter_to_plot),
    x = "Theoretical Quantiles",
    y = "Sample Quantiles"
  ) +
  theme_minimal())
unique(subset_dfDO$station)

##SPC
parameter_to_plot <- "spc"
subset_dfspc <- combined_df_long[combined_df_long$Parameter == parameter_to_plot, ]
(ggplot(subset_dfspc, aes(sample = Value)) +
  stat_qq() +
  stat_qq_line(color = "red") +
  facet_wrap(~station, scales = "free") +  # One plot per station
  labs(
    title = paste("QQ Plots for", parameter_to_plot),
    x = "Theoretical Quantiles",
    y = "Sample Quantiles"
  ) +
  theme_minimal())
unique(subset_dfDO$station)


#ph
parameter_to_plot <- "ph"
subset_dfph <- combined_df_long[combined_df_long$Parameter == parameter_to_plot, ]
(ggplot(subset_dfph, aes(sample = Value)) +
  stat_qq() +
  stat_qq_line(color = "red") +
  facet_wrap(~station, scales = "free") +  # One plot per station
  labs(
    title = paste("QQ Plots for", parameter_to_plot),
    x = "Theoretical Quantiles",
    y = "Sample Quantiles"
  ) +
  theme_minimal())

#fluor
parameter_to_plot <- "fluorescence"
subset_dfflu <- combined_df_long[combined_df_long$Parameter == parameter_to_plot, ]
(ggplot(subset_dfflu, aes(sample = Value)) +
  stat_qq() +
  stat_qq_line(color = "red") +
  facet_wrap(~station, scales = "free") +  # One plot per station
  labs(
    title = paste("QQ Plots for", parameter_to_plot),
    x = "Theoretical Quantiles",
    y = "Sample Quantiles"
  ) +
  theme_minimal())


##turb
parameter_to_plot <- "turbidity"
subset_dfturb <- combined_df_long[combined_df_long$Parameter == parameter_to_plot, ]
(ggplot(subset_dfflu, aes(sample = Value)) +
  stat_qq() +
  stat_qq_line(color = "red") +
  facet_wrap(~station, scales = "free") +  # One plot per station
  labs(
    title = paste("QQ Plots for", parameter_to_plot),
    x = "Theoretical Quantiles",
    y = "Sample Quantiles"
  ) +
  theme_minimal())

#water temp -keeps taking out two stations
parameter_to_plot <- "watertemperature"
subset_dfWT <- combined_df_long[combined_df_long$Parameter == parameter_to_plot, ]
(ggplot(subset_dfflu, aes(sample = Value)) +
  stat_qq() +
  stat_qq_line(color = "red") +
  facet_wrap(~station, scales = "free") +  # One plot per station
  labs(
    title = paste("QQ Plots for", parameter_to_plot),
    x = "Theoretical Quantiles",
    y = "Sample Quantiles"
  ) +
  theme_minimal())



## here is a code for all do not like the scale though
# Parameters to compare
parameters <- c("dissolvedoxygen", "watertemperature", "turbidity", "ph", "spc", "fluorescence")  # List of parameters to plot

# Create a list of plots for each parameter
plots <- lapply(parameters, function(param) {
  # Subset data for each parameter
  subset_df <- combined_df_long[combined_df_long$Parameter == param, ]
  
  # Generate QQ plots for the chosen parameter across all stations
  ggplot(subset_df, aes(sample = Value)) +
    stat_qq() +
    stat_qq_line(color = "red") +
    facet_wrap(~station, scales = "free") +  # One plot per station
    labs(
      title = paste("QQ Plots for", param),
      x = "Theoretical Quantiles",
      y = "Sample Quantiles"
    ) +
    theme_minimal()
})

# Combine all the plots into a single grid for easy viewing
library(gridExtra)
do.call(grid.arrange, c(plots, ncol = 2))  # Adjust 'ncol' as needed




```




```{r}
# Assuming combined_df is your continuous water quality dataframe

# Define the date range
start_date <- as.POSIXct("2019-07-01 00:00:00")
end_date <- as.POSIXct("2019-10-07 23:59:59")

# Filter data within the specified date range and for the selected stations
filtered_data <- combined_df %>%
  filter(date_time >= start_date & date_time <= end_date &
         station %in% c("GZB", "GZL"))

# Calculate percent differences for selected columns
percent_diff <- filtered_data %>%
  group_by(date_time) %>%
  summarize(
    do_diff = (first(dissolvedoxygen)-last(dissolvedoxygen))/first(dissolvedoxygen),
    spc_diff = (first(spc)-last(spc))/first(spc),
    ph_diff = (first(ph)-last(ph))/first(ph),
    temp_diff = (first(watertemperature)-last(watertemperature))/first(watertemperature),
    turbidity_diff = (first(turbidity)-last(turbidity))/first(turbidity),
    fluorescence_diff = (first(fluorescence)-last(fluorescence))/first(fluorescence)
  )

# Display the percent differences
print(percent_diff)
view(percent_diff)
# Load the necessary library if not already loaded
# install.packages("ggplot2")
library(ggplot2)

# Assuming percent_diff is the data frame containing percent differences

# Melt the data for better plotting
melted_data <- tidyr::gather(percent_diff, parameter, percent_diff, -date_time)

view(melted_data)
# Create a line plot
ggplot(melted_data, aes(x = date_time, y = percent_diff,)) +
  geom_line() +
  facet_wrap(~parameter, scales = "free_y") +
  labs(title = "Percent Differences Over Time",
       x = "Datetime",
       y = "Percent Difference") +
  theme_minimal()


### plot data with just both stations
ggplot(combined_df, aes(x = date_time, y= watertemperature, color = station)) + geom_line()
ggplot(combined_df, aes(x = date_time, y= spc, color = station)) + geom_line()


### 
gz = filter(combined_df, station%in%c("GZB", "GZL"))

gz = mutate(gz, year = year(date_time)) %>% 
  filter(!is.na(year))

ggplot(gz, aes(x = date_time, y =watertemperature, color = station)) + geom_line() +facet_wrap(~year, scales = "free_x")

ggplot(gz, aes(x = date_time, y =spc, color = station)) + geom_line() +facet_wrap(~year, scales = "free_x")
```
```{r}
## plot absolute differences and zoom on time periods all exploratory plots, when you see signals like spc investigate what times of the time more likely to be different, times of the day, times of day for certain parameters and seasonally and then include when gate actions are in effects not

```
 trying absolute difference plots   
 
```{r}

#get absolute differences trying to mimic code from line 442

# Calculate absolute differences
absolute_diff <- filtered_data %>%
  group_by(date_time) %>%
  summarize(
    do_diff = abs(first(dissolvedoxygen) - last(dissolvedoxygen)),
    spc_diff = abs(first(spc) - last(spc)),
    ph_diff = abs(first(ph) - last(ph)),
    temp_diff = abs(first(watertemperature) - last(watertemperature)),
    turbidity_diff = abs(first(turbidity) - last(turbidity)),
    fluorescence_diff = abs(first(fluorescence) - last(fluorescence))
  )


print(absolute_diff)
##not sure what melting the data does but did it before for 'better plotting' 
melted_data_ab <- tidyr::gather(absolute_diff, parameter, absolute_diff, -date_time)
view(melted_data_ab)


#filter dataset for 1st gate action in 2018 one month before and after

ggplot(absolute_diff, aes(x = date_time, y = spc_diff)) + geom_line()
labs(title = "Percent Differences Over Time",
       x = "Datetime",
       y = "Absolute Difference") +
  theme_minimal()
```
 
 