---
title: "SMSCG Comparision"
author: "Michelle Nelson"
date: "2024-01-25"
output: html_document
---

# Overview
The goal of this comparison is to compare the two sets of sites that SMSCG uses to monitor the action plan. 
The comparison will be between: Hunter Cut (HUN)vs Montezuma Buoy (GZM) and Grizzly Bay Buoy (GZB)vs Grizzly Bay Pile (GZL)


```{r}
### make sure you have the right libraries installed: tidyverse, etc
#install.packages("svglite")
```
1. libraries 
```{r, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
# Your plotting code here

knitr::opts_chunk$set(fig.show = "hide")

library(svglite)
library(tidyverse)
library("ggpubr")
library(lubridate)
library(wql)
library(RColorBrewer)
library(cder)
library(dplyr)
library(readr)
library(here)
source(here("helpful_functions.R"))
```

#2 Load in data. Now I have 6 different data frames for all the data needed(4 years of comparisions with 2018 being on one 2 site comparision)
```{r}
### Load in the data running these functions #make sure to run Helpful r functions 1st!

dfGZLediALL <- get_edi_file(1177, "GZL")[[1]]


##dfGZLediALL <- dfGZLediALL %>% filter(year(date)>=2018)

dfGZBfinal <- abs_path_emp("Water Quality/SMSCG/GZB_final.csv")%>% read.csv(.)

dfHUNALL <- abs_path_emp("Water Quality/SMSCG/HUN_All.csv")%>% read.csv(.)

dfGZMALL <- abs_path_emp("Water Quality/SMSCG/GZM_All.csv")%>% read.csv(.)

# not needed go it from EDI df_GZL2023 <- abs_path_emp("Water Quality/SMSCG/GZL_2023_data.csv")%>% read.csv(.)

dfGZB <- abs_path_emp("Water Quality/SMSCG/GZB_data.csv")%>% read.csv(.)




```

#3 reformat dates
```{r}
###GZL2018-2023

dfGZLediALL <- dfGZLediALL %>% mutate(date_time = paste(date, time)) %>% #combine the date and time columns
  mutate(year = year(date_time)) #add a year column

#view(dfGZLediALL)## all good need to model all other dataframes like this one (column order, names, remove bad qcd data etc)
summary(dfGZLediALL) ### 2018-2023

###GZB2018 is dfGZB


## trying this code to match column name
dfGZBfinal3yrs <- dfGZBfinal %>% 
  mutate(DATETIME = as.POSIXct(DATETIME, format = '%m/%d/%Y %H:%M', tz = 'UTC'),
         year = year(DATETIME))
#view(dfGZBfinal3yrs)


## GZL already done for 2018, 2021, 2022 will need 2023 below

##HUN
dfHUNALL3 <- dfHUNALL %>%
  mutate(DATETIME = as.POSIXct(DATETIME, format = '%m/%d/%Y %H:%M', tz = 'UTC'),
         year = year(DATETIME)) ### this worked! just needed to see that the original datetime didnt have seconds and same column name
#View(dfHUNALL3)

### GZM all years 21-23

dfGZMALL3 <- dfGZMALL %>%
  mutate(DATETIME = as.POSIXct(DATETIME, format = '%m/%d/%Y %H:%M', tz = 'UTC'),
         year = year(DATETIME))
#view(dfGZMALL)

 ## now all dates should be the same so I can combine the full dataset later
 dfGZBfinal <- dfGZBfinal %>% mutate(DATE.TIME = as.POSIXct(DATETIME, format = "%Y-%m-%d %H:%M:%S"))
dfGZLediALL <-dfGZLediALL %>% mutate(date_time = as.POSIXct(date_time, format = "%Y-%m-%d %H:%M:%S"))
### not needed when I first started 2023 wasnt published yet now it is
#df_GZL2023 <- df_GZL2023 %>% mutate(date_time = as.POSIXct(date_time, format = "%Y-%m-%d %H:%M:%S"))
dfGZBfinal3yrs <- dfGZBfinal3yrs %>% mutate(DATETIME = as.POSIXct(DATETIME, format = "%Y-%m-%d %H:%M:%S"))
dfGZMALL3 <- dfGZMALL3 %>% mutate(DATETIME = as.POSIXct(DATETIME, format = "%Y-%m-%d %H:%M:%S"))
dfHUNALL3 <- dfHUNALL3 %>% mutate(DATETIME = as.POSIXct(DATETIME, format = "%Y-%m-%d %H:%M:%S"))


## will need to rename datetime in last 3 to the same as first three above can do when cleaning data and ordering column names
## not sure if this was done later or not...

```
#4 clean out bad data from WQA datasets, and CEMP already has NAs where bad data is. 
-Replace all values that have Bad ("B" and "X") codes with NAs

```{r}

## 
# three WQA datasets: dfGZMALL3, dfGZBfinal3yrs, HUNALL3

# dfGZBfinal3yrs
colnames(dfGZBfinal3yrs)


#check fluor first
unique(dfGZBfinal3yrs$Chl...QAQC.Flag) ## has all 4 codes want to make sure first that there isnt a lot of unchecked data.
## just showed me the flag types
#Chl_a_ug_L_counts <- dfGZBfinal3yrs %>%
 # group_by(Chl...QAQC.Flag) %>%
  #summarise(NumDistinctFlags = n_distinct(Chl...QAQC.Flag))
#View(Chl_a_ug_L_counts)

##Chl_a_ug_L_counts <- dfGZBfinal3yrs %>%
#  group_by(Chl...QAQC.Flag) %>%
 # summarise(NumOccurrences = n())
#view(Chl_a_ug_L_counts)

#flourescence changing all B,X and U flags to NAs ####THIS WORKED REPLACING VALUES WITH NA


summary(dfGZBfinal3yrs)


dfGZBfinal3yrs$Chl.a..µg.L. <- replace(dfGZBfinal3yrs$Chl.a..µg.L., dfGZBfinal3yrs$Chl...QAQC.Flag=="B", NA)
dfGZBfinal3yrs$Chl.a..µg.L. <- replace(dfGZBfinal3yrs$Chl.a..µg.L., dfGZBfinal3yrs$Chl...QAQC.Flag=="X", NA)
dfGZBfinal3yrs$Chl.a..µg.L. <- replace(dfGZBfinal3yrs$Chl.a..µg.L., dfGZBfinal3yrs$Chl...QAQC.Flag=="U", NA)
dfGZBfinal3yrs$Chl.a..µg.L. <- replace(dfGZBfinal3yrs$Chl.a..µg.L., dfGZBfinal3yrs$Chl...QAQC.Flag=="M", NA)

#turbidity # the colnames are ridiculous should replace now but didnt
unique(dfGZBfinal3yrs$Turbidity...QAQC.Flag)
dfGZBfinal3yrs$Turbidity..NTU. <- replace(dfGZBfinal3yrs$Turbidity..NTU., dfGZBfinal3yrs$Turbidity...QAQC.Flag=="M", NA)
dfGZBfinal3yrs$Turbidity..NTU. <- replace(dfGZBfinal3yrs$Turbidity..NTU., dfGZBfinal3yrs$Turbidity...QAQC.Flag=="X", NA)


###Spc
unique(dfGZBfinal3yrs$SpCond...QAQC.Flag)
dfGZBfinal3yrs$SpCond..µS.cm. <- replace(dfGZBfinal3yrs$SpCond..µS.cm.,dfGZBfinal3yrs$SpCond...QAQC.Flag                                           =="M", NA)
dfGZBfinal3yrs$SpCond..µS.cm. <- replace(dfGZBfinal3yrs$SpCond..µS.cm.,dfGZBfinal3yrs$SpCond...QAQC.Flag                                           =="X", NA)


#### temp
unique(dfGZBfinal3yrs$Temp...QAQC.Flag)
dfGZBfinal3yrs$Temp...C. <- replace(dfGZBfinal3yrs$Temp...C., dfGZBfinal3yrs$Temp...QAQC.Flag=="M", NA)
dfGZBfinal3yrs$Temp...C. <- replace(dfGZBfinal3yrs$Temp...C., dfGZBfinal3yrs$Temp...QAQC.Flag=="X", NA)


### pH
unique(dfGZBfinal3yrs$pH...QAQC.Flag)
dfGZBfinal3yrs$pH <- replace(dfGZBfinal3yrs$pH, dfGZBfinal3yrs$pH...QAQC.Flag=="M", NA)
dfGZBfinal3yrs$pH <- replace(dfGZBfinal3yrs$pH, dfGZBfinal3yrs$pH...QAQC.Flag=="X", NA)


### DO
unique(dfGZBfinal3yrs$DO...QAQC.Flag)
dfGZBfinal3yrs$DO..mg.L. <- replace(dfGZBfinal3yrs$DO..mg.L.,dfGZBfinal3yrs$DO...QAQC.Flag=="M", NA)
dfGZBfinal3yrs$DO..mg.L. <- replace(dfGZBfinal3yrs$DO..mg.L.,dfGZBfinal3yrs$DO...QAQC.Flag=="X", NA)


#### DFGZMALL
#temp
unique(dfGZMALL3$Temp...QAQC.Flag)
dfGZMALL3$Temp...C. <- replace(dfGZMALL3$Temp...C., dfGZMALL3$Temp...QAQC.Flag=="M", NA)
dfGZMALL3$Temp...C. <- replace(dfGZMALL3$Temp...C., dfGZMALL3$Temp...QAQC.Flag=="X", NA)
dfGZMALL3$Temp...C. <- replace(dfGZMALL3$Temp...C., dfGZMALL3$Temp...QAQC.Flag=="U", NA)

#spc
unique(dfGZMALL3$SpCond...QAQC.Flag)
dfGZMALL3$SpCond..µS.cm. <- replace(dfGZMALL3$SpCond..µS.cm., dfGZMALL3$SpCond...QAQC.Flag=="M", NA)
dfGZMALL3$SpCond..µS.cm. <- replace(dfGZMALL3$SpCond..µS.cm., dfGZMALL3$SpCond...QAQC.Flag=="X", NA)

#DO
unique(dfGZMALL3$DO...QAQC.Flag)
dfGZMALL3$DO..mg.L. <- replace(dfGZMALL3$DO..mg.L.,dfGZMALL3$DO...QAQC.Flag=="M", NA)
dfGZMALL3$DO..mg.L. <- replace(dfGZMALL3$DO..mg.L.,dfGZMALL3$DO...QAQC.Flag=="X", NA)

#ph
unique(dfGZMALL3$pH...QAQC.Flag)
dfGZMALL3$pH <- replace(dfGZMALL3$pH, dfGZMALL3$pH...QAQC.Flag=="M", NA)
dfGZMALL3$pH <- replace(dfGZMALL3$pH, dfGZMALL3$pH...QAQC.Flag=="X", NA)

#turb
unique(dfGZMALL3$Turbidity...QAQC.Flag)
dfGZMALL3$Turbidity..NTU. <- replace(dfGZMALL3$Turbidity..NTU., dfGZMALL3$Turbidity...QAQC.Flag=="X", NA)
dfGZMALL3$Turbidity..NTU. <- replace(dfGZMALL3$Turbidity..NTU., dfGZMALL3$Turbidity...QAQC.Flag=="U", NA)

#fluor
unique(dfGZMALL3$Chl...QAQC.Flag)

dfGZMALL3$Chl.a..µg.L. <- replace(dfGZMALL3$Chl.a..µg.L., dfGZMALL3$Chl...QAQC.Flag=="X", NA)
dfGZMALL3$Chl.a..µg.L. <- replace(dfGZMALL3$Chl.a..µg.L., dfGZMALL3$Chl...QAQC.Flag=="U", NA)

summary(dfGZMALL3)

selected_column <- 'Chl...QAQC.Flag'

cat("Summary for", selected_column, ":\n")
print(table(dfGZMALL3[[selected_column]]))

#### just realized there is no B code for WQA annoying except SP WEIRD

##HUNALL3
summary(dfHUNALL3)

# List of columns to summarize
columns_to_check <- c("Temp...QAQC.Flag., dfHUNALL3", "SpCond...QAQC.Flag", "DO...QAQC.Flag", "pH...QAQC.Flag", "Turbidity...QAQC.Flag", "Chl...QAQC.Flag")

# Loop through the columns and count the flags
lapply(columns_to_check, function(col) {
  cat("Counts for", col, ":\n")
  print(table(dfHUNALL3[[col]]))
  cat("\n")
})


#temp
unique(dfHUNALL3$Temp...QAQC.Flag)
dfHUNALL3$Temp...C. <- replace(dfHUNALL3$Temp...C., dfHUNALL3$Temp...QAQC.Flag=="X", NA)
dfHUNALL3$Temp...C. <- replace(dfHUNALL3$Temp...C., dfHUNALL3$Temp...QAQC.Flag=="U", NA)
#spc
dfHUNALL3$SpCond..µS.cm. <- replace(dfHUNALL3$SpCond..µS.cm., dfHUNALL3$SpCond...QAQC.Flag=="X", NA)
dfHUNALL3$SpCond..µS.cm. <- replace(dfHUNALL3$SpCond..µS.cm., dfHUNALL3$SpCond...QAQC.Flag=="U", NA)
dfHUNALL3$SpCond..µS.cm. <- replace(dfHUNALL3$SpCond..µS.cm., dfHUNALL3$SpCond...QAQC.Flag=="B", NA)

##DO
dfHUNALL3$DO..mg.L. <- replace(dfHUNALL3$DO..mg.L., dfHUNALL3$DO...QAQC.Flag=="X", NA)
dfHUNALL3$DO..mg.L. <- replace(dfHUNALL3$DO..mg.L., dfHUNALL3$DO...QAQC.Flag=="M", NA)

##ph
dfHUNALL3$pH <- replace(dfHUNALL3$pH, dfHUNALL3$pH...QAQC.Flag=="X", NA)
dfHUNALL3$pH <- replace(dfHUNALL3$pH, dfHUNALL3$pH...QAQC.Flag=="M", NA)

##turb
dfHUNALL3$Turbidity..NTU. <- replace(dfHUNALL3$Turbidity..NTU., dfHUNALL3$Turbidity...QAQC.Flag=="X", NA)
dfHUNALL3$Turbidity..NTU. <- replace(dfHUNALL3$Turbidity..NTU., dfHUNALL3$Turbidity...QAQC.Flag=="U", NA)
dfHUNALL3$Turbidity..NTU. <- replace(dfHUNALL3$Turbidity..NTU., dfHUNALL3$Turbidity...QAQC.Flag=="M", NA)

##fluor
dfHUNALL3$Chl.a..µg.L. <- replace(dfHUNALL3$Chl.a..µg.L., dfHUNALL3$Chl...QAQC.Flag=="X", NA)
dfHUNALL3$Chl.a..µg.L. <- replace(dfHUNALL3$Chl.a..µg.L., dfHUNALL3$Chl...QAQC.Flag=="U", NA)
dfHUNALL3$Chl.a..µg.L. <- replace(dfHUNALL3$Chl.a..µg.L., dfHUNALL3$Chl...QAQC.Flag=="M", NA)

selected_column <- 'Chl...QAQC.Flag'

cat("Summary for", selected_column, ":\n")
print(table(dfHUNALL3[[selected_column]]))

view(dfHUNALL3)
```
#5 should arrange colnames and take out slopes and QC flag columns

```{r}
### remove unwanted columns in WQA and rename to CEMP file column names
colnames(dfHUNALL3)
# Assuming 'dfHUNALL3', 'dfGZMALL3', and 'dfGZBfinal3years' are your DataFrames
# Replace these with your actual DataFrames or load them from files

# List of columns to be kept
columns_to_keep <- c("STATION.NAME", "DATETIME", "DO..mg.L.", "SpCond..µS.cm.", "pH", "Temp...C.", "Turbidity..NTU.", "Chl.a..µg.L.")

# Load the dplyr package if not already loaded
# install.packages("dplyr")
library(dplyr)

# Function to keep specified columns in a dataframe and rename it
keep_columns_and_rename <- function(df, columns, new_name_suffix) {
  new_name <- paste0(deparse(substitute(df)), new_name_suffix)
  return(assign(new_name, df %>% select(all_of(columns)), envir = .GlobalEnv))
}

# Keep specified columns in each dataframe and rename them
dfHUNALL3F <- keep_columns_and_rename(dfHUNALL3, columns_to_keep, "F")
dfGZMALL3F <- keep_columns_and_rename(dfGZMALL3, columns_to_keep, "F")
dfGZBfinal3yrsF <- keep_columns_and_rename(dfGZBfinal3yrs, columns_to_keep, "F")


```
#6 rename colnames in WQA to match CEMP add date time year col

```{r}
# wanted column names
#colnames(df_GZL2023)
# New column names
new_column_names <- c("station", "date_time", "dissolvedoxygen", "spc", "ph", "watertemperature", "turbidity", "fluorescence")

# Function to rename columns in a dataframe
rename_columns <- function(df, new_names) {
  colnames(df) <- new_names
  return(df)
}

# Rename columns in each dataframe

dfHUNALL3F <- rename_columns(dfHUNALL3F, new_column_names)
dfGZMALL3F <- rename_columns(dfGZMALL3F, new_column_names)
dfGZBfinal3yrsF <- rename_columns(dfGZBfinal3yrsF, new_column_names)

## add date, time, year col to match CEMP

library(dplyr)

# Function to add new date, time, and year columns based on the DateTime column
add_datetime_columns <- function(df) {
  df <- df %>%
    mutate(date = as.Date(date_time),
           time = format(date_time, "%H:%M:%S"),
           year = lubridate::year(date_time))
  return(df)
}

# Add new date, time, and year columns to each dataframe
dfHUNALL3F <- add_datetime_columns(dfHUNALL3F)
dfGZMALL3F <- add_datetime_columns(dfGZMALL3F)
dfGZBfinal3yrsF <- add_datetime_columns(dfGZBfinal3yrsF)


```

#7 make sure columns in same order
```{r}


# Reference order of columns
reference_order <- c("date_time", "date", "time", "year", "station", "dissolvedoxygen", "spc", "ph", "watertemperature", "turbidity", "fluorescence")

# Load the dplyr package if not already loaded
# install.packages("dplyr")
library(dplyr)

# Function to rearrange columns in a dataframe based on reference order
rearrange_columns <- function(df, reference_order) {
  df <- select(df, all_of(reference_order))
  return(df)
}

# Rearrange columns in each dataframe
dfHUNALL3F <- rearrange_columns(dfHUNALL3F, reference_order)
dfGZMALL3F <- rearrange_columns(dfGZMALL3F, reference_order)
dfGZBfinal3yrsF <- rearrange_columns(dfGZBfinal3yrsF, reference_order)
dfGZBFINAL <- rearrange_columns(dfGZB, reference_order)
dfGZLediALL <- rearrange_columns(dfGZLediALL, reference_order)
#df_GZL2023 <- rearrange_columns(df_GZL2023, reference_order)


### need to change WQA station names to acronyms
## never did this
## cant get this to work without adding a column dfHUNALL3F <- dfHUNALL3F %>%
 ## mutate(station = if_else(station == "Hunter Cut", "HUN", station))


```


#8 need to add new data from 2024 GZM, HUN, GZL, GZB- repeat steps from #2 did not need to do NAs was done manually
```{r}
#load in data
GZM24 <- abs_path_emp("Water Quality/SMSCG/GZM_2024_CLEANEDDATA.csv")%>% read.csv(.)
GZB24 <- abs_path_emp("Water Quality/SMSCG/GZB_2024_CLEANED DATA.csv")%>% read.csv(.)
HUN24 <- abs_path_emp("Water Quality/SMSCG/HUN_2024_CLEANED DATA.csv")%>% read.csv(.)
GZL24 <- abs_path_emp("Water Quality/SMSCG/GZL_2024_CLEANED DATA.csv")%>% read.csv(.)

# Ensure the Date.Time column is correctly formatted
data_frames <- list(GZB24 = GZB24, GZM24 = GZM24, HUN24 = HUN24, GZL24 = GZL24)

# Add seconds and convert Date.Time to POSIXct
data_frames <- lapply(data_frames, function(df) {
  if (!"Date.Time" %in% colnames(df)) {
    stop("Column 'Date.Time' not found in one or more data frames.")
  }
  
  # Append seconds if missing
  df$Date.Time <- paste0(df$Date.Time, ":00")
  
  # Convert from the modified format to the desired format
  df$Date.Time <- as.POSIXct(df$Date.Time, format = "%m/%d/%Y %H:%M:%S", tz = "UTC")
  return(df)
})

# Extract data frames back
GZB24 <- data_frames$GZB24
GZM24 <- data_frames$GZM24
HUN24 <- data_frames$HUN24
GZL24 <- data_frames$GZL24

# Check the conversion
lapply(data_frames, function(df) head(df$Date.Time))

#need matching colnames and station column


#change colnames
# Define the mapping of old column names to new column names
column_mapping <- c(
  "Date.Time" = "date_time",
  "Dissolved.Oxygen" = "dissolvedoxygen",
  "Specific.Conductance" = "spc",
  "Chlorophyll" = "fluorescence",
  "Turbidity" = "turbidity",
  "Water.Temperature" = "watertemperature",
  "pH" = "ph"
)

# Safely rename columns before adding the station column
GZB24 <- GZB24 %>%
  rename(
    date_time = Date.Time,
    dissolvedoxygen = Dissolved.Oxygen,
    spc = Specific.Conductance,
    fluorescence = Chlorophyll,
    turbidity = Turbidity,
    watertemperature = Water.Temperature,
    ph = pH
  ) %>%
  mutate(station = "GZB")

GZM24 <- GZM24 %>%
  rename(
    date_time = Date.Time,
    dissolvedoxygen = Dissolved.Oxygen,
    spc = Specific.Conductance,
    fluorescence = Chlorophyll,
    turbidity = Turbidity,
    watertemperature = Water.Temperature,
    ph = pH
  ) %>%
  mutate(station = "GZM")
colnames(HUN24)
HUN24 <- HUN24 %>%
  rename(
    date_time = Date.Time,
    dissolvedoxygen = Dissolved.Oxygen,
    spc = Specific.Conductance,
    fluorescence = Chlorophyll,
    turbidity = Turbidity,
    watertemperature = Water.Temperature,
    ph = pH
  ) %>%
  mutate(station = "HUN")

GZL24 <- GZL24 %>%
  rename(
    date_time = Date.Time,
    dissolvedoxygen = Dissolved.Oxygen,
    spc = Specific.Conductance,
    fluorescence = Chlorophyll,
    turbidity = Turbidity,
    watertemperature = Water.Temperature,
    ph = pH
  ) %>%
  mutate(station = "GZL")

# Combine all the dataframes into one
combined_df24 <- bind_rows(GZB24, GZM24, HUN24, GZL24)

# Check the final column names
colnames(combined_df24)

##### need to run the NA code

```



#9 combine all dataframes
```{r}
## make sure dates are all the same character type


library(dplyr)


library(lubridate)

# Convert date_time columns to POSIXct type with consistent format and remove unwanted columns/ reorder the rest right after:

dfGZBFINAL <- dfGZBFINAL %>% mutate(date_time = as.POSIXct(paste(date_time, "00:00:00"), format = "%Y-%m-%d %H:%M:%S")) #date
dfGZBFINAL2 <- dfGZBFINAL %>%  select(-date, -time, -year) #removing columns
str(dfGZBFINAL2)

dfGZLediALL <- dfGZLediALL %>% mutate(date_time = as.POSIXct(date_time, format = " %H:%M:%S"))
dfGZLediALL2 <- dfGZLediALL %>%  select(-date, -time, -year) #removing columns



## dont need anymore df_GZL2023 <- df_GZL2023 %>% mutate(date_time = as.POSIXct(date_time, format = "%Y-%m-%d %H:%M:%S"))
#df_GZL20232 <- df_GZL2023 %>%  select(-date, -time, -year) #removing columns
#str(df_GZL20232)


str(dfGZBfinal3yrsF)
head(dfGZBfinal3yrsF)
dfGZBfinal3yrs2 <- dfGZBfinal3yrsF %>% select(-date, -time, -year) ## wont run keeps making the new DF have no data
## trying to kepp the columns I want. 
dfGZBfinal3yrs2 <- dfGZBfinal3yrsF %>% select(date_time, station, dissolvedoxygen, spc, ph, turbidity, fluorescence)
dfGZBfinal3yrs2<- dfGZBfinal3yrs2 %>% mutate(date_time = as.POSIXct(date_time, format = "%Y-%m-%d %H:%M:%S"))


###
dfGZMALL3F <- dfGZMALL3F %>% select(-date, -time, -year)
dfGZMALL3F <- dfGZMALL3F %>% select(date_time, station, dissolvedoxygen, spc, ph, turbidity, fluorescence)
dfGZMALL3F <- dfGZMALL3F %>% mutate(date_time = as.POSIXct(date_time, format = "%Y-%m-%d %H:%M:%S"))

####

dfHUNALL3F <- dfHUNALL3F %>% select(-date, -time, -year)
dfHUNALL3F <- dfHUNALL3F %>% select(date_time, station, dissolvedoxygen, spc, ph, turbidity, fluorescence)
dfHUNALL3F <- dfHUNALL3F %>% mutate(date_time = as.POSIXct(date_time, format = "%Y-%m-%d %H:%M:%S"))




# Combine the dataframes using bind_rows
combined_df <- bind_rows(dfGZBFINAL2, dfGZLediALL2, dfGZBfinal3yrs2, dfGZMALL3F, dfHUNALL3F)
str(combined_df)
###### YAY IT WORKED

###Now I want to rename the station

unique(combined_df$station)

# Rename specific stations
combined_df <- combined_df %>%
  mutate(station = case_when(
    station == "Grizzly Bay East" ~ "GZB",
    station == "Montezuma Slough Mouth" ~ "GZM",
    station == "Hunter Cut" ~ "HUN",
    TRUE ~ station  # Keep other stations unchanged
  ))

unique(combined_df$station)

### okay now I need to combine the combined_df with combined_df24 while reordering the column names
# Reorder the columns in existing_df to match the column order of combined_df
combined_df <- combined_df %>%
  select(date_time, station, dissolvedoxygen, spc, ph, watertemperature, turbidity, fluorescence)

# Now combine the dataframes
combined_df <- bind_rows(combined_df24, combined_df)

# Check the final combined dataframe
str(combined_df)





```
 #10 comparision 2018 GZL and GZB 
 
```{r}
library(dplyr)
library(lubridate)
library(ggplot2)

str(combined_df)

filtered_dataGZL <- combined_df %>% 
  filter(station == "GZL",
         date_time >=as.Date("2018-07-01"),
         date_time<=as.Date("2018-10-06"))


  
GZL2018<-ggplot(data = filtered_dataGZL, aes(x = date_time, y = spc )) + geom_line(color = "red") + labs(title = "GZL Specific conductivity gate action 2018", 
                                 x = "Date", y = "Specific Conductivity") + theme_minimal()

print(GZL2018)


ggplot(data = filtered_dataGZL, aes(x = date_time, y = watertemperature )) + geom_line(color = "blue") + labs(title = "GZL Water Temperature gate action 2018", 
                                 x = "Date", y = "Water Temperature") + theme_minimal()

```
```{r}
### lets see what the two sites look like plotted together

filtered_dataGZLGZB <- combined_df %>% 
  filter(station == c("GZL", "GZB"),
         date_time >=as.Date("2018-07-01"),
         date_time <=as.Date("2018-10-06"))


  
ggplot(data = filtered_dataGZLGZB, aes(x = date_time, y = spc, color = station )) + geom_line() +geom_point() + labs(title = "GZL and GZB Specific conductivity gate action 2018", x = "Date", y = "Specific Conductivity", color = "Station") + theme_minimal()


ggplot(data = filtered_dataGZLGZB, aes(x = date_time, y = spc, color = station )) + geom_line() + labs(title = "GZL and GZB Specific conductivity gate action 2018", x = "Date", y = "Specific Conductivity", color = "Station") + theme_minimal()

###decided to put all comparision sites together on plots per parameter below is working code, may want to just smooth out the line and tweak the way the plots look but continue to


```


#11 QQPLOTS per parameter for each station

```{r}
# Load ggplot2 library
library(ggplot2)
### in order to do QQplots/facet_grid I need to reshape the data into long format
library(tidyr)


# Reshaping data to long format
combined_df_long <- combined_df %>%
  pivot_longer(
    cols = c(dissolvedoxygen, spc, ph, watertemperature, turbidity, fluorescence),
    names_to = "Parameter",
    values_to = "Value"
  )

###missing or NA values
combined_df_long <- na.omit(combined_df_long)



# Generate QQ Plots

#DO
# Assuming 'combined_df_long' is your long-format dataframe
parameter_to_plot <- "dissolvedoxygen"  # Replace with your desired parameter
 
# Subset the data for the chosen parameter
subset_dfDO <- combined_df_long[combined_df_long$Parameter == parameter_to_plot, ]
 
# Generate QQ plots for the chosen parameter across all stations
(qqplotdo <- ggplot(subset_dfDO, aes(sample = Value)) +
  stat_qq() +
  stat_qq_line(color = "red") +
  facet_wrap(~station, scales = "free") +  # One plot per station
  labs(
    title = paste("QQ Plots for", parameter_to_plot),
    x = "Theoretical Quantiles",
    y = "Sample Quantiles"
  ) +
  theme_minimal())
#unique(subset_dfDO$station)


#how to save remaning QQplots change filename and path
ggsave(plot = qqplotdo, filename = abs_path_emp("Water Quality/SMSCG/QQplots/qqplotdo.svg"),
       width = 14, height = 10)

```


```{r}
##SPC
parameter_to_plot <- "spc"
subset_dfspc <- combined_df_long[combined_df_long$Parameter == parameter_to_plot, ]
(ggplot(subset_dfspc, aes(sample = Value)) +
  stat_qq() +
  stat_qq_line(color = "red") +
  facet_wrap(~station, scales = "free") +  # One plot per station
  labs(
    title = paste("QQ Plots for", parameter_to_plot),
    x = "Theoretical Quantiles",
    y = "Sample Quantiles"
  ) +
  theme_minimal())
unique(subset_dfDO$station)


#ph
parameter_to_plot <- "ph"
subset_dfph <- combined_df_long[combined_df_long$Parameter == parameter_to_plot, ]
(ggplot(subset_dfph, aes(sample = Value)) +
  stat_qq() +
  stat_qq_line(color = "red") +
  facet_wrap(~station, scales = "free") +  # One plot per station
  labs(
    title = paste("QQ Plots for", parameter_to_plot),
    x = "Theoretical Quantiles",
    y = "Sample Quantiles"
  ) +
  theme_minimal())

#fluor
parameter_to_plot <- "fluorescence"
subset_dfflu <- combined_df_long[combined_df_long$Parameter == parameter_to_plot, ]
(ggplot(subset_dfflu, aes(sample = Value)) +
  stat_qq() +
  stat_qq_line(color = "red") +
  facet_wrap(~station, scales = "free") +  # One plot per station
  labs(
    title = paste("QQ Plots for", parameter_to_plot),
    x = "Theoretical Quantiles",
    y = "Sample Quantiles"
  ) +
  theme_minimal())


##turb
parameter_to_plot <- "turbidity"
subset_dfturb <- combined_df_long[combined_df_long$Parameter == parameter_to_plot, ]
(ggplot(subset_dfflu, aes(sample = Value)) +
  stat_qq() +
  stat_qq_line(color = "red") +
  facet_wrap(~station, scales = "free") +  # One plot per station
  labs(
    title = paste("QQ Plots for", parameter_to_plot),
    x = "Theoretical Quantiles",
    y = "Sample Quantiles"
  ) +
  theme_minimal())

#water temp 
parameter_to_plot <- "watertemperature"
subset_dfWT <- combined_df_long[combined_df_long$Parameter == parameter_to_plot, ]
(ggplot(subset_dfflu, aes(sample = Value)) +
  stat_qq() +
  stat_qq_line(color = "red") +
  facet_wrap(~station, scales = "free") +  # One plot per station
  labs(
    title = paste("QQ Plots for", parameter_to_plot),
    x = "Theoretical Quantiles",
    y = "Sample Quantiles"
  ) +
  theme_minimal())



## here is a code for all do not like the scale though
# Parameters to compare
parameters <- c("dissolvedoxygen", "watertemperature", "turbidity", "ph", "spc", "fluorescence")  # List of parameters to plot

# Create a list of plots for each parameter
plots <- lapply(parameters, function(param) {
  # Subset data for each parameter
  subset_df <- combined_df_long[combined_df_long$Parameter == param, ]
  
  # Generate QQ plots for the chosen parameter across all stations
  ggplot(subset_df, aes(sample = Value)) +
    stat_qq() +
    stat_qq_line(color = "red") +
    facet_wrap(~station, scales = "free") +  # One plot per station
    labs(
      title = paste("QQ Plots for", param),
      x = "Theoretical Quantiles",
      y = "Sample Quantiles"
    ) +
    theme_minimal()
})

# Combine all the plots into a single grid for easy viewing
library(gridExtra)
do.call(grid.arrange, c(plots, ncol = 2))  # Adjust 'ncol' as needed




```




```{r}
# Assuming final_combined_df is your continuous water quality dataframe

# Define the date range
start_date <- as.POSIXct("2019-07-01 00:00:00")
end_date <- as.POSIXct("2019-10-07 23:59:59")

# Filter data within the specified date range and for the selected stations
filtered_data <- combined_df %>%
  filter(date_time >= start_date & date_time <= end_date &
         station %in% c("GZB", "GZL"))

# Calculate percent differences for selected columns
percent_diff <- filtered_data %>%
  group_by(date_time) %>%
  summarize(
    do_diff = (first(dissolvedoxygen)-last(dissolvedoxygen))/first(dissolvedoxygen),
    spc_diff = (first(spc)-last(spc))/first(spc),
    ph_diff = (first(ph)-last(ph))/first(ph),
    temp_diff = (first(watertemperature)-last(watertemperature))/first(watertemperature),
    turbidity_diff = (first(turbidity)-last(turbidity))/first(turbidity),
    fluorescence_diff = (first(fluorescence)-last(fluorescence))/first(fluorescence)
  )

# Display the percent differences
print(percent_diff)
view(percent_diff)
# Load the necessary library if not already loaded
# install.packages("ggplot2")
library(ggplot2)

# Assuming percent_diff is the data frame containing percent differences

# Melt the data for better plotting
melted_data <- tidyr::gather(percent_diff, parameter, percent_diff, -date_time)

view(melted_data)
# Create a line plot
ggplot(melted_data, aes(x = date_time, y = percent_diff,)) +
  geom_line() +
  facet_wrap(~parameter, scales = "free_y") +
  labs(title = "Percent Differences Over Time",
       x = "Datetime",
       y = "Percent Difference") +
  theme_minimal()


### plot data with just both stations
ggplot(combined_df, aes(x = date_time, y= watertemperature, color = station)) + geom_line()
ggplot(combined_df, aes(x = date_time, y= spc, color = station)) + geom_line()


### 
gz = filter(combined_df, station%in%c("GZB", "GZL"))

gz = mutate(gz, year = year(date_time)) %>% 
  filter(!is.na(year))

ggplot(gz, aes(x = date_time, y =watertemperature, color = station)) + geom_line() +facet_wrap(~year, scales = "free_x")

ggplot(gz, aes(x = date_time, y =spc, color = station)) + geom_line() +facet_wrap(~year, scales = "free_x")
```
```{r}
## plot absolute differences and zoom on time periods all exploratory plots, when you see signals like spc investigate what times of the time more likely to be different, times of the day, times of day for certain parameters and seasonally and then include when gate actions are in effects not

```
 trying absolute difference plots   
 
```{r}
#get absolute differences trying to mimic code from line 442

# Calculate absolute differences
absolute_diff <- filtered_data %>%
  group_by(date_time) %>%
  summarize(
    do_diff = abs(first(dissolvedoxygen) - last(dissolvedoxygen)),
    spc_diff = abs(first(spc) - last(spc)),
    ph_diff = abs(first(ph) - last(ph)),
    temp_diff = abs(first(watertemperature) - last(watertemperature)),
    turbidity_diff = abs(first(turbidity) - last(turbidity)),
    fluorescence_diff = abs(first(fluorescence) - last(fluorescence))
  )


print(absolute_diff)
##not sure what melting the data does but did it before for 'better plotting' 
melted_data_ab <- tidyr::gather(absolute_diff, parameter, absolute_diff, -date_time)
view(melted_data_ab)


#filter dataset for 1st gate action in 2018 one month before and after

ggplot(absolute_diff, aes(x = date_time, y = spc_diff)) + geom_line()
labs(title = "Percent Differences Over Time",
       x = "Datetime",
       y = "Absolute Difference") +
```


#Vivian's timeseries code

```{r}

### 15m
### Start saving graphs with svg files so they're vector-based and not pixel based (for better resolution when zooming in)


## Faceted all stations 
## Note that these are all based off the wide format data. The averaged graphs later are based on long format.
(pltpHall <- ggplot(data = combined_df, aes(x = date_time, y = ph )) + 
    geom_line(color = "darkorange") + 
    labs(x = "Date", y = "pH") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltpHall, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/15m/pH.svg"),
       width = 14, height = 10)

(pltspcall <- ggplot(data = combined_df, aes(x = date_time, y = spc )) + 
    geom_line(color = "red") + 
    labs(x = "Date", y = "Specific Conductivity") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltspcall, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/15m/spc.svg"),
       width = 14, height = 10)

(plttempall <- ggplot(data = combined_df, aes(x = date_time, y = watertemperature )) + 
    geom_line(color = "blue") + 
    labs(x = "Date", y = "Water Temperature") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = plttempall, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/15m/temp.svg"),
       width = 14, height = 10)

(pltchlall <- ggplot(data = combined_df, aes(x = date_time, y = fluorescence )) + 
    geom_line(color = "darkgreen") + 
    labs(x = "Date", y = "Chlorophyll Fluorescence") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltchlall, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/15m/chl.svg"),
       width = 14, height = 10)

(pltdoall <- ggplot(data = combined_df, aes(x = date_time, y = dissolvedoxygen )) + 
    geom_line(color = "purple") + 
    labs(x = "Date", y = "Dissolved Oxygen") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltdoall, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/15m/do.svg"),
       width = 14, height = 10)

(pltturball <- ggplot(data = combined_df, aes(x = date_time, y = turbidity )) + 
    geom_line(color = "brown") + 
    labs(x = "Date", y = "Turbidity") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltturball, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/15m/turb.svg"),
       width = 14, height = 10)

### Salinity only graphs of gate actions

GateAction1 <- combined_df %>% 
  filter(station==c("GZL", "GZB"),
         # This way of filtering stations didn't work in long format, but fine here
         date_time >=as.Date("2018-08-01"),
         date_time<=as.Date("2018-09-06"))
(pltGateAction1spc <- ggplot(data = GateAction1, aes(x = date_time, y = spc )) + 
    geom_line(color = "red") + 
    labs(title= "2018 Gate Action", x = "Date", y = "Specific Conductivity") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltGateAction1spc, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/15m/GateAction1spc.svg"),
       width = 14, height = 10)

GateAction2 <- combined_df %>% 
  filter(date_time >=as.Date("2021-09-01"),
         date_time<=as.Date("2021-12-24"))
(pltGateAction2spc <- ggplot(data = GateAction2, aes(x = date_time, y = spc )) + 
    geom_line(color = "red") + 
    labs(title= "2021 Gate Action", x = "Date", y = "Specific Conductivity") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltGateAction2spc, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/15m/GateAction2spc.svg"),
       width = 14, height = 10)

GateAction3 <- combined_df %>% 
  filter(date_time >=as.Date("2022-09-01"),
         date_time<=as.Date("2023-01-05"))
(pltGateAction3spc <- ggplot(data = GateAction3, aes(x = date_time, y = spc )) + 
    geom_line(color = "red") + 
    labs(title = "2022 Gate Action", x = "Date", y = "Specific Conductivity") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltGateAction3spc, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/15m/GateAction3spc.svg"),
       width = 14, height = 10)

GateAction4 <- combined_df %>% 
  filter(date_time >=as.Date("2023-08-15"),
         date_time<=as.Date("2023-10-17"))
(pltGateAction4spc <- ggplot(data = GateAction4, aes(x = date_time, y = spc )) + 
    geom_line(color = "red") + 
    labs(title= "2023 Gate Action", x = "Date", y = "Specific Conductivity") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltGateAction4spc, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/15m/GateAction4spc.svg"),
       width = 14, height = 10)

# This graph isn't working because the data file I'm using doesn't yet have the 2024 data
GateAction5 <- combined_df %>% 
  filter(date_time >=as.Date("2024-09-06"),
         date_time<=as.Date("2024-09-30"))
(pltGateAction5spc <- ggplot(data = GateAction5, aes(x = date_time, y = spc )) + 
    geom_line(color = "red") + 
    labs(title= "2024 Gate Action", x = "Date", y = "Specific Conductivity") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltGateAction5spc, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/15m/GateAction5spc.svg"),
       width = 14, height = 10)
```
 
```{r}

###1HR

combined_df1h <- combined_df_long %>%
  # mutate(date = date(date_time), hour = hour(date_time)) %>%
  mutate(date_hour = ymd_hms(paste0(date(date_time), " ", hour(date_time), ":00:00"))) %>%
  group_by(date_hour,station,Parameter) %>%
  summarise(hourlyavg = mean(Value))


## Faceted all stations
(pltpHall1h <- ggplot(data = filter(combined_df1h, Parameter=="ph"), aes(x = date_hour, y = hourlyavg)) + 
    geom_line(color = "darkorange") + 
    labs(title = "pH, all stations, 1h avg",x = "Date", y = "pH") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltpHall1h, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/1h/pH.svg"),
       width = 14, height = 10)

(pltspcall1h <- ggplot(data = filter(combined_df1h, Parameter=="spc"), aes(x = date_hour, y = hourlyavg )) + 
    geom_line(color = "red") + 
    labs(title = "Salinity, all stations, 1h avg", x = "Date", y = "Specific Conductivity") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltspcall, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/1h/spc.svg"),
       width = 14, height = 10)

(plttempall1h <- ggplot(data = filter(combined_df1h, Parameter=="watertemperature"), aes(x = date_hour, y = hourlyavg)) + 
    geom_line(color = "blue") + 
    labs(title = "Water Temperature, all stations, 1h avg", x = "Date", y = "Water Temperature") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = plttempall, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/1h/temp.svg"),
       width = 14, height = 10)

(pltchlall1h <- ggplot(data = filter(combined_df1h, Parameter=="fluorescence"), aes(x = date_hour, y =  hourlyavg)) + 
    geom_line(color = "darkgreen") + 
    labs(title = "Chlorophyll Fluorescence, all stations, 1h avg", x = "Date", y = "Chlorophyll Fluorescence") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltchlall1h, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/1h/chl.svg"),
       width = 14, height = 10)

(pltdoall1h <- ggplot(data = filter(combined_df1h, Parameter=="dissolvedoxygen"), aes(x = date_hour, y = hourlyavg )) + 
    geom_line(color = "purple") + 
    labs(title = "Dissolved Oxygen, all stations, 1h avg", x = "Date", y = "Dissolved Oxygen") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltdoall1h, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/1h/do.svg"),
       width = 14, height = 10)

(pltturball1h <- ggplot(data = filter(combined_df1h, Parameter=="turbidity"), aes(x = date_hour, y = hourlyavg )) + 
    geom_line(color = "brown") + 
    labs(x = "Date", y = "Turbidity") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltturball1h, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/1h/turb.svg"),
       width = 14, height = 10)

### Salinity only graphs of gate actions
GateAction1_1h <- combined_df1h %>% 
  filter(Parameter == "spc",
         station == "GZL" | station == "GZB",
         # I found that it didn't like the argument station == c("GZL","GZB") but the above syntax worked
         date_hour >= as.Date("2018-08-01"),
         date_hour <= as.Date("2018-09-06"))
(pltGateAction1spc1h <- ggplot(data = GateAction1_1h, aes(x = date_hour, y = hourlyavg )) + 
    geom_line(color = "red") + 
    labs(title= "2018 Gate Action, 1h avg", x = "Date", y = "Specific Conductivity") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltGateAction1spc1h, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/1h/GateAction1spc.svg"),
       width = 14, height = 10)

GateAction2_1h <- combined_df1h %>% 
  filter(Parameter == "spc",
         date_hour >=as.Date("2021-09-01"),
         date_hour<=as.Date("2021-12-24"))
(pltGateAction2spc1h <- ggplot(data = GateAction2_1h, aes(x = date_hour, y = hourlyavg )) + 
    geom_line(color = "red") + 
    labs(title= "2021 Gate Action, 1h avg", x = "Date", y = "Specific Conductivity") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltGateAction2spc1h, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/1h/GateAction2spc.svg"),
       width = 14, height = 10)

GateAction3_1h <- combined_df1h %>% 
  filter(Parameter == "spc",
         date_hour >=as.Date("2022-09-01"),
         date_hour<=as.Date("2023-01-05"))
(pltGateAction3spc1h <- ggplot(data = GateAction3_1h, aes(x = date_hour, y = hourlyavg )) + 
    geom_line(color = "red") + 
    labs(title = "2022 Gate Action, 1h avg", x = "Date", y = "Specific Conductivity") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltGateAction3spc1h, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/1h/GateAction3spc.svg"),
       width = 14, height = 10)

GateAction4_1h <- combined_df1h %>% 
  filter(Parameter == "spc",
         date_hour >=as.Date("2023-08-15"),
         date_hour <=as.Date("2023-10-17"))
(pltGateAction4spc1h <- ggplot(data = GateAction4_1h, aes(x = date_hour, y = hourlyavg )) + 
    geom_line(color = "red") + 
    labs(title= "2023 Gate Action, 1h avg", x = "Date", y = "Specific Conductivity") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltGateAction4spc1h, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/1h/GateAction4spc.svg"),
       width = 14, height = 10)

# This graph isn't working because the data file I'm using doesn't yet have the 2024 data
GateAction5_1h <- combined_df1h %>% 
  filter(Parameter == "spc",
         date_hour>=as.Date("2024-09-06"),
         date_hour<=as.Date("2024-09-30"))
(pltGateAction5spc1h <- ggplot(data = GateAction5_1h, aes(x = date_hour, y = hourlyavg )) + 
    geom_line(color = "red") + 
    labs(title= "2024 Gate Action, 1h avg", x = "Date", y = "Specific Conductivity") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltGateAction5spc1h, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/1h/GateAction5spc.svg"),
       width = 14, height = 10)
```
 
```{r}
##24


combined_df24h <- combined_df_long %>%
  mutate(date_time = ymd(date_time)) %>%
  group_by(date_time,station,Parameter) %>%
  summarise(dailyavg = mean(Value))


(pltpHall24h <- ggplot(data = filter(combined_df24h, Parameter=="ph"), aes(x = date_time, y = dailyavg )) + 
    geom_line(color = "darkorange") + 
    labs(title = "ph, Daily Averages",x = "Date", y = "pH") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltpHall24h, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/24h/pH.svg"),
       width = 14, height = 10)

(pltspcall24h <- ggplot(data = filter(combined_df24h, Parameter=="spc"), aes(x = date_time, y = dailyavg )) + 
    geom_line(color = "red") + 
    labs(title="Salinity, Daily Averages", x = "Date", y = "Specific Conductivity") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltspcall24h, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/24h/spc.svg"),
       width = 14, height = 10)

(plttempall24h <- ggplot(data = filter(combined_df24h, Parameter=="watertemperature"), aes(x = date_time, y = dailyavg )) + 
    geom_line(color = "blue") + 
    labs(title= "Water Temperature, Daily averages", x = "Date", y = "Water Temperature") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = plttempall24h, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/24h/temp.svg"),
       width = 14, height = 10)

(pltchlall24h <- ggplot(data = filter(combined_df24h, Parameter == "fluorescence"), aes(x = date_time, y = dailyavg )) + 
    geom_line(color = "darkgreen") + 
    labs(title= "Chlorophyll Fluorescence, Daily averages", x = "Date", y = "Chlorophyll Fluorescence") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltchlall24h, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/24h/chl.svg"),
       width = 14, height = 10)

(pltdoall24h <- ggplot(data = filter(combined_df24h, Parameter == "dissolvedoxygen"), aes(x = date_time, y = dailyavg )) + 
    geom_line(color = "purple") + 
    labs(title= "Dissolved Oxygen, Daily averages", x = "Date", y = "Dissolved Oxygen") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltdoall24h, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/24h/do.svg"),
       width = 14, height = 10)

(pltturball24h <- ggplot(data = filter(combined_df24h,Parameter == "turbidity"), aes(x = date_time, y = dailyavg )) + 
    geom_line(color = "brown") + 
    labs(title= "Turbidity, Daily averages", x = "Date", y = "Turbidity") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltturball24h, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/24h/turb.svg"),
       width = 14, height = 10)

### Salinity only graphs of gate actions
GateAction1_24h <- combined_df24h %>% 
  filter(Parameter == "spc",
         station == "GZL" | station == "GZB",
         date_time >=as.Date("2018-08-01"),
         date_time<=as.Date("2018-09-06"))
(pltGateAction1spc24h <- ggplot(data = GateAction1_24h, aes(x = date_time, y = dailyavg )) + 
    geom_line(color = "red") + 
    labs(title= "2018 Gate Action", x = "Date", y = "Specific Conductivity") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltGateAction1spc24h, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/24h/GateAction1spc.svg"),
       width = 14, height = 10)

GateAction2_24h <- combined_df24h %>% 
  filter(Parameter=="spc",
         date_time >=as.Date("2021-09-01"),
         date_time<=as.Date("2021-12-24"))
(pltGateAction2spc24h <- ggplot(data = GateAction2_24h, aes(x = date_time, y = dailyavg )) + 
    geom_line(color = "red") + 
    labs(title= "2021 Gate Action", x = "Date", y = "Specific Conductivity") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltGateAction2spc24h, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/24h/GateAction2spc.svg"),
       width = 14, height = 10)

GateAction3_24h <- combined_df24h %>% 
  filter(Parameter=="spc",
         date_time >=as.Date("2022-09-01"),
         date_time<=as.Date("2023-01-05"))
(pltGateAction3spc24h <- ggplot(data = GateAction3_24h, aes(x = date_time, y = dailyavg)) + 
    geom_line(color = "red") + 
    labs(title = "2022 Gate Action", x = "Date", y = "Specific Conductivity") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltGateAction3spc24h, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/24h/GateAction3spc.svg"),
       width = 14, height = 10)

GateAction4_24h <- combined_df24h %>% 
  filter(Parameter=="spc",
         date_time >=as.Date("2023-08-15"),
         date_time<=as.Date("2023-10-17"))
(pltGateAction4spc24h <- ggplot(data = GateAction4_24h, aes(x = date_time, y = dailyavg )) + 
    geom_line(color = "red") + 
    labs(title= "2023 Gate Action", x = "Date", y = "Specific Conductivity") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltGateAction4spc24h, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/24h/GateAction4spc.svg"),
       width = 14, height = 10)

# This graph isn't working because the data file I'm using doesn't yet have the 2024 data
GateAction5_24h <- combined_df24h %>% 
  filter(Parameter=="spc",
         date_time >=as.Date("2024-09-06"),
         date_time<=as.Date("2024-09-30"))
(pltGateAction5spc24h <- ggplot(data = GateAction5_24h, aes(x = date_time, y = dailyavg )) + 
    geom_line(color = "red") + 
    labs(title= "2024 Gate Action", x = "Date", y = "Specific Conductivity") + 
    facet_grid(station~., scales = "free_y")+
    theme_light())
ggsave(plot = pltGateAction5spc24h, filename = abs_path_emp("Water Quality/SMSCG/TimeSeriesGraphs/24h/GateAction5spc.svg"),
       width = 14, height = 10)
```
 
 